---
title: "Pikes Peak data"
author: "Rachel Havranek"
date: "10/9/2017"
output:
  html_document: default
  pdf_document: default
---
Load Necessary Libraries. The plotly library, in conjunction with command ggplotly(), gives us interactive plots. can't remember what the grid library does right now.  
```{r load libraries, message=FALSE, include = FALSE}
library(tidyverse)
library (plotly)
base.directory<-"~/Documents/MSc Publication Work/R work"
```

1. Read in ZHe and AFT data that have all been formatted uniformly. Its easiest to have sample name (e.g. elevation) and then replicate parsed into 2 separate columns. This makes is easier to pull out spurious data later without having to manipulate the input file (and potentially permanently lose that data)
```{r load data, message=FALSE, warning=FALSE}
Pikes_Data<- read_csv("~/Documents/MSc Publication Work /R work/Pikes_Data_for_R .csv")
Mount_Evans <- read_csv("~/Documents/MSc Publication Work /R work/Evans Data.csv") 
Longs_Peak<- read_csv("~/Documents/MSc Publication Work /R work/Longs Peak .csv")
AFT_Data<-read_csv("~/Documents/MSc Publication Work /R work/AFT_Data.csv")
```

# Data Wrangling
1. Set a legend title
2. Separate out AFT data so I can plot them separately 
3. combine all ZHe data (includes ME ammonium data right now)
4. Filter my Mount Evans data based on dissolution method 
```{r  data wrangling}
legend_title<-"Elevation (m)" 

Pikes_AFT<-filter(AFT_Data, Peak=="Pikes Peak")
Longs_AFT<-filter(AFT_Data, Peak=="Longs Peak")
Evans_AFT<-filter(AFT_Data, Peak=="Mount Evans")

ZHe_all<-bind_rows(Pikes_Data, Mount_Evans, Longs_Peak)
```

# Pikes Peak 
This section makes plots for:   
1. Pikes Peak Date-eU  
2. Pikes Peak Elevation - date  
3. Pikes Peak Elevation vs. date with each point colored by eU  
4. Pikes Peak date vs. grain size   
3. Pikes Peak AFT data (Kelley and Chapin, 2004)  
```{r Plot Pikes}
#### Date eU ####
PP_DeU<-ggplot (data=Pikes_Data, aes(x=eU, y=date)) +  
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_errorbarh(aes(xmin=eU-eU_unc, xmax=eU+eU_unc)) +
  geom_point(aes(fill=Elevation), pch=22, size=4) +  
  viridis::scale_fill_viridis(option = "magma", limits = c(2000, 4500))+
  geom_vline(xintercept = 150, linetype= "dashed")  + 
  geom_vline(xintercept = 350, linetype = "dashed") +  
  geom_vline(xintercept = 500,linetype="dashed")  + 
  geom_vline(xintercept = 900,linetype="dashed")  + 
  labs(x="eU (ppm)", y = "Date (Ma)", title = "Pikes Peak" ) +  
  scale_x_continuous(expand =c(0,0), limits=c(0,2400), breaks=seq(0, 2400, 400)) + 
  scale_y_continuous(expand =c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  theme_classic() +
  theme(
    panel.border = element_rect(fill=NA, colour = "black", size = 1),
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.title.x = element_text(face="bold", size=12),
    axis.title.y= element_text(face="bold", size=12),
    legend.text = element_text(size = 10),
    axis.text = element_text(color = "black", size = 10), 
    plot.title = element_text(size = 14, hjust = 0.5))+
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))


####Elevation Date####
#Elevation vs. Date with each point colored by eU 
PP_ED_byeU<-ggplot (data=Pikes_Data, aes(date, Elevation))+
  geom_errorbarh(aes(xmin=date-uncertainty, xmax=date+uncertainty), color = 'black', height=0)+
  geom_point(aes(fill=eU), shape=22, size=4)+
  viridis::scale_fill_viridis(option = "viridis", limits = c(0,2000))+
  geom_point(data=Pikes_AFT, aes(AFT_date, Elevation), pch=15, size=4)+
  theme_classic()+
  labs(x="Date (Ma)", y = "Elevation (m)", title = "Pikes Peak") +  
  scale_x_continuous(expand =c(0,0), limits=c(0,800), breaks=seq(0, 800, 200)) + 
  scale_y_continuous(expand =c(0,0), limits = c(2000,4500), breaks=seq(2000, 4500, 500))+
  theme(
   panel.border = element_rect(fill=NA, colour = "black", size = 1),
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.title.x = element_text(face="bold", size=12),
    axis.title.y= element_text(face="bold", size=12),
    legend.text = element_text(size = 10),
    axis.text = element_text(color = "black", size = 10), 
    legend.position = c(.9, 0.75),
    plot.title = element_text(size = 14, hjust = 0.5))+
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))

#ggsave("PPelevation_date.pdf", width = 4  , height = 3, units = "in", dpi=300)

####Grain Size####
#Grain size w/ color as Elevation 
PP_grainsize_elev<-ggplot (data=Pikes_Data, aes(Grain_size, date))+
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_point (aes(fill=Elevation), shape=22, size =4)+
  viridis::scale_fill_viridis(option = "magma", limits = c(2000, 4500))+
  theme_classic()+
  scale_y_continuous(expand =c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  scale_x_continuous(expand =c(0,0), limits=c(0,140), breaks=seq(0, 140, 30)) + 
  labs(x="Grain Size", y = "Date", title = "Pikes Peak") +  
  theme(
    panel.border=element_rect(fill=NA, size = 1),
    text = element_text(size = 12),
    legend.position = "none",
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.text = element_text(color = "black", size = 12)) +
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight =2))+
  theme(plot.title = element_text(size = 14, hjust = 0.5))
#ggsave("PPdate_grain3.pdf", width = 4  , height = 3, units = "in", dpi=300)

#Grain size vs. eU 
PP_grainsize_eU<-ggplot (data=Pikes_Data, aes (Grain_size, eU))+
  geom_errorbar(aes(ymin=eU-eU_unc, ymax=eU+eU_unc)) +
  geom_point (aes(fill=Elevation), shape=22, size=4)+
  viridis::scale_fill_viridis(option = "magma", limits = c(2000, 4500))+
  theme_classic()+
  scale_x_continuous(expand =c(0,0), limits = c(0,140), breaks=seq(0, 140, 30)) +
  scale_y_continuous(expand =c(0,0), limits=c(0,2400), breaks=seq(0, 2400, 400)) + 
  labs(x="Grain size (µm)", y = "eU", title = "Pikes Peak") +  
  theme(
    panel.border=element_rect(fill=NA,size = 1),
    text = element_text(size = 12),
    legend.position = "none", 
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.text = element_text(color = "black", size = 12)) +
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))+
  theme(plot.title = element_text(size = 14, hjust = 0.5))
#ggsave("PP eU vs. r.pdf", width = 4  , height = 3, units = "in", dpi=300)

####AFT#### 
PPAFT<-ggplot(data=Pikes_AFT, aes(x=AFT_date, y=Elevation))+
  geom_point(pch=0, size=3)+
  geom_errorbarh(data=Pikes_AFT, aes(xmin=(AFT_date-date_error), xmax=(AFT_date+date_error), height=0))+
  scale_x_continuous(limits=c(0,800), breaks=seq(0, 800, 200)) + 
  scale_y_continuous(limits = c(2000,4500), breaks=seq(2000, 4500, 500)) +
  labs(x="Date (Ma)", y="Elevation (m)") +
  theme_classic(axis.title.x = element_text(face="bold", size=10), 
    axis.title.y=element_text(face="bold", size=10), 
    axis.text = element_text(colour = "black"),
    legend.position = c(.85, 0.75))+
#ggsave("PP_AFT.pdf", width=5.5, height = 4.5, units = "in", dpi=300) 

```

```{r extra pikes plots, include= FALSE}
#Date eU of other subsets
ramanZHe <- filter(Pikes_Data, Elevation=="2084"|Elevation=="2907"|Elevation=="3971")
ramanZhe_deu<-ggplot (data=ramanZHe, aes(x=eU, y=date)) + 
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_point(aes(colour=Sample_Name), pch=15, size=4) +  
  scale_colour_manual(values=c("#d73037", "#fee090", "#91bfbd"))+
  geom_errorbarh(aes(xmin=eU-eU_unc, xmax=eU+eU_unc)) +
  geom_vline(xintercept = 200, linetype= "dashed")  + 
  geom_vline(xintercept = 400, linetype= "dashed")  + 
  geom_vline(xintercept = 600, linetype = "dashed") +  
  geom_vline(xintercept = 1000,linetype="dashed")  + 
  labs(x="eU (ppm)", y = "Date (Ma)", title = "Pikes Peak" ) +  
  scale_x_continuous(expand =c(0,0), limits=c(0,2400), breaks=seq(0, 2400, 400)) + 
  scale_y_continuous(expand =c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  theme_classic() +
  theme(
    panel.border=element_rect(fill=NA,size = 1),
    text = element_text(size = 12),
    legend.text = element_text(size = 10), 
    axis.text = element_text(color = "black")) +
    guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))+
    theme(plot.title = element_text(size = 14, hjust = 0.5))

top3 <- filter(Pikes_Data, Sample_Name=="PP4297"|Sample_Name=="PP3971"|Sample_Name=="PP3597")
top3_plot<-ggplot (data=top3, aes(x=eU, y=date)) +  
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_errorbarh(aes(xmin=eU-eU_unc, xmax=eU+eU_unc)) +
  geom_point(aes(colour=Elevation), pch=15, size=4) +  
  scale_color_distiller(palette = "Paired", guide="legend")+
  geom_vline(xintercept = 250, linetype= "dashed")  + 
  #geom_vline(xintercept = 600, linetype = "dashed") +  
  geom_vline(xintercept = 850,linetype="dashed")  + 
  labs(x="eU (ppm)", y = "Date (Ma)", title = "Pikes Peak" ) +  
  scale_x_continuous(expand =c(0,0), limits=c(0,2400), breaks=seq(0, 2400, 400)) + 
  scale_y_continuous(expand =c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  theme_classic() +
  theme(
    panel.border=element_rect(fill=NA,size = 2),
    text = element_text(size = 12),
    legend.text = element_text(size = 10), 
    axis.line = element_line(colour=NA),
    axis.text = element_text(color = "black")) +
    guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))+
    theme(plot.title = element_text(size = 14, hjust = 0.5))


top4_plot<-ggplot (data=PP_top4, aes(x=eU, y=date)) +  
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_errorbarh(aes(xmin=eU-eU_unc, xmax=eU+eU_unc)) +
  geom_point(aes(colour=Elevation), pch=15, size=4) +  
  scale_color_distiller(palette = "Paired", guide="legend")+
  geom_vline(xintercept = 250, linetype= "dashed")  + 
  geom_vline(xintercept = 350, linetype = "dashed") + 
  geom_vline(xintercept = 600, linetype = "dashed") +
  geom_vline(xintercept = 850,linetype="dashed")  + 
  geom_vline(xintercept = 1200,linetype="dashed")  + 
  labs(x="eU (ppm)", y = "Date (Ma)", title = "Pikes Peak" ) +  
  scale_x_continuous(expand =c(0,0), limits=c(0,2400), breaks=seq(0, 2400, 400)) + 
  scale_y_continuous(expand =c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  theme_classic() +
  theme(
    panel.border=element_rect(fill=NA,size = 2),
    text = element_text(size = 12),
    legend.text = element_text(size = 10), 
    axis.line = element_line(colour = NA),
    axis.text = element_text(color = "black")) +
    guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))+
    theme(plot.title = element_text(size = 14, hjust = 0.5))

#Elevation - Date 
PPED<-ggplot (data=Pikes_Data, aes(x=date, y=Elevation))  + 
  geom_point(aes(colour=Elevation), pch=19, size=4) + 
  scale_colour_distiller(palette = "RdYlBu", direction=1)+
  geom_errorbarh(aes(xmin=date-uncertainty, xmax=date+uncertainty), color = 'black', size=0.5, height=0) +
  labs(x="Date (Ma)", y = "Elevation (m)", title = "Pikes Peak Elevation vs. Date" ) +  
  scale_x_continuous(expand =c(0,0), limits=c(0,800), breaks=seq(0, 800, 200)) + 
  scale_y_continuous(expand =c(0,0), limits = c(2000,4500), breaks=seq(2000, 4500, 500)) +
  theme_classic()+
  theme(
    panel.border=element_rect(fill=NA,size = 1),
    text = element_text(size = 12),
    legend.text = element_text(size = 10), 
    axis.text = element_text(color = "black")) +
    guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))+
    theme(plot.title = element_text(size = 14, hjust = 0.5))
#ggsave("PPelevation_date.pdf", width = 4  , height = 4, units = "in", dpi=300)




#Grain size w/ color designation as eU 
PP_grainsize_eU<-ggplot (data=Pikes_Data, aes(Grain_size, date))+
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_point (aes(colour=eU), shape=15, size=4)+
  scale_colour_distiller(palette = "Spectral", direction = -1)  +
  theme_classic()+
  scale_y_continuous(expand =c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  scale_x_continuous(expand =c(0,0), limits=c(0,140), breaks=seq(0, 140, 30)) + 
  labs(x="Grain Size", y = "Date", title = "Pikes Peak") +  
  theme(
    panel.border=element_rect(fill=NA,size = 1),
    text = element_text(size = 12),
    legend.text = element_text(size = 10), 
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.text = element_text(color = "black", size = 12)) +
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))+
  theme(plot.title = element_text(size = 14, hjust = 0.5))
#ggsave("PPdate_grain1.pdf", width = 4  , height = 3, units = "in", dpi=300)

```

This chunk calculates what I want for my Hefty model 
```{r}
Pikes_Data <- mutate(Pikes_Data, bindata= cut(eU, c(0,150,350,500,900,2500))) #these are my bin cutoffs

hefty_flatlist <- Pikes_Data %>% 
  filter (replicate != "z32") %>% #I filtered out this daa point because its ~300 Ma younger than everything else in that bin
  group_by(bindata) %>% 
    summarize( 
      N = n(),
      RawDate_mean =  round (mean(Raw_Date), digits = 2),
      Rawdate_15percent = round (0.15*mean(Raw_Date), digits = 2),
      Rawdate_SD = round (sd(Raw_Date), digits = 2),
      CorrDate_mean = round(mean(date), digits = 2),
      CorrDate_15percent = round(0.15*mean(date),digits = 2),
      CorrDate_SD = round (sd(date), digits = 2),
      mean_rs = round(mean(Grain_size), digits = 2),
      U = round (mean(U), digits = 2),
      Th = round (mean(Th), digits = 2),
      Sm = round (mean(Sm), digits = 2),
      eU = round (mean(eU), digits = 2),
      He = round (mean(He), digits = 2),
      FT = round (mean(FT), digits = 2),
      )

write.csv(hefty_flatlist, file="Pikes Hefty Flatlist.csv")
ungroup(Pikes_Data)

```

This section makes plots for: 
1. Mt. Evans Date -eU. As of 3/4/18 this plot only plots HF dissolution data (data=ME_normal). It plots on an axis from 0 to 2400 eu to best match other 2 peaks - this excludes 2 high eU dates which are captured on Me_DeU_full 
2. A full data set inset (includes high eU data). Again, as of 3/4/18 this plot excludes NH4 dissolution data 
3. Mt. Evans Elevation - date as of 3/17/18 this plot only plots HF dissoluaiton data (data=ME_normal)
4. Mt evans Elevation - date (07/20/18 - only normal dissolution)
5. Mt Evans date vs. grain size 
6. Mt. Evans AFT 
```{r Plot Mount Evans Data}
####Date eU####
#main data fram
ME_DeU<-ggplot (data=ME_normal, aes(x=eU, y=date)) + 
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_errorbarh(aes(xmin=eU-eU_unc, xmax=eU+eU_unc)) +
  geom_vline(xintercept = 400, linetype = "dashed") +  
  geom_vline(xintercept = 700,linetype="dashed")  + 
  geom_vline(xintercept = 1600,linetype="dashed")  + 
  geom_point(aes(fill=Elevation), pch=24, size=4) +  
  viridis::scale_fill_viridis(option = "magma", limits = c(2000,4500))+
  labs(x="eU (ppm)", y = "Date (Ma)", title = "Mt. Evans" ) +  
  scale_x_continuous(expand=c(0,0), limits=c(0,2400), breaks=seq(0, 2400, 400)) + 
  scale_y_continuous(expand=c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  theme_classic() +
  theme(
    panel.border = element_rect(fill=NA, colour = "black", size = 1),
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.title.x = element_text(face="bold", size=12),
    axis.title.y= element_text(face="bold", size=12),
    legend.text = element_text(size = 10),
    axis.text = element_text(color = "black", size = 10), 
    legend.position = "none",
    plot.title = element_text(size = 14, hjust = 0.5))
#ggsave("MEdate_eU.pdf", width = 4  , height = 3, units = "in", dpi=300)

# all data
ME_DeU_full<-ggplot (data=ME_normal, aes(x=eU, y=date)) + 
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black') + 
  geom_errorbarh(aes(xmin=eU-eU_unc, xmax=eU+eU_unc), height=0) +
  geom_point(aes(fill=Elevation), pch=24, size=1) +  
  viridis::scale_fill_viridis(option = "magma",  limits = c(2000,4500))+
  labs(x="eU (ppm)", y = "Date (Ma)") +  
  scale_x_continuous(expand=c(0,0), limits=c(0,6600), breaks=seq(0, 6600, 3000)) + 
  scale_y_continuous(expand=c(0,0), limits = c(0,800), breaks=seq(0, 800, 400)) +
  theme_classic() +
  theme(
    panel.border = element_rect(fill=NA, colour = "black", size = 1),
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.title.x = element_text(face="bold", size=6),
    axis.title.y= element_text(face="bold", size=6),
    legend.text = element_text(size = 6),
    axis.text = element_text(color = "black", size = 8), 
    legend.position = "none"
    )
#ggsave("ME_full.pdf", width=1.3, height = 1, units="in")

####Elevation Date####
ME_ED_byeU<-ggplot (data=ME_normal, aes(date, Elevation))+
  geom_errorbarh(aes(xmin=date-uncertainty, xmax=date+uncertainty), color = 'black', height=0)+
  geom_point(aes(fill=eU), shape=24, size=3)+
  viridis::scale_fill_viridis(option = "viridis", limits=c(0,2000))+
  geom_point(data=Evans_AFT, aes(AFT_date, Elevation), pch=17, size=3)+
  theme_classic()+
  labs(x="Date (Ma)", y = "Elevation (m)", title = "Mount Evans") +  
  scale_x_continuous(expand =c(0,0), limits=c(0,800), breaks=seq(0, 800, 200)) + 
  scale_y_continuous(expand =c(0,0), limits = c(2000,4500), breaks=seq(2000, 4500, 500))+
  theme(
    panel.border = element_rect(fill=NA, colour = "black", size = 1),
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.title.x = element_text(face="bold", size=10),
    axis.title.y= element_text(face="bold", size=10),
    legend.text = element_text(size = 7),
    axis.text = element_text(color = "black", size = 8), 
    legend.position = c(.9, 0.75),
    plot.title = element_text(size = 14, hjust = 0.5))
#ggsave("MEelevation_date.pdf", width = 4  , height = 3, units = "in", dpi=300)


####Grain Size####
#Grain size w/ color as Elevation 
ME_grainsize_elev<-ggplot (data=ME_normal, aes(Grain_size, date))+
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_point (aes(fill=Elevation), shape=24, size =4)+
  viridis::scale_fill_viridis(option = "magma", limits = c(2000,4500))+
  theme_classic()+
  scale_y_continuous(expand =c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  scale_x_continuous(expand =c(0,0), limits=c(0,140), breaks=seq(0, 140, 30)) + 
  labs(x="Grain Size (µm)", y = "Date (Ma)", title = "Mt. Evans") +  
  theme(
    panel.border=element_rect(fill=NA,size = 1),
    text = element_text(size = 12),
    legend.position = "none", 
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.text = element_text(color = "black", size = 12)) +
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight =2))+
  theme(plot.title = element_text(size = 14, hjust = 0.5))
#ggsave("ME_rdate.pdf", width = 4  , height = 3, units = "in")

#Grain size vs. eU
ME_reU_full<-ggplot (data=ME_normal, aes(Grain_size, eU)) + 
  geom_errorbar(aes(ymin=eU-eU_unc, ymax=eU+eU_unc)) +
  geom_point(aes(fill=Elevation), pch=24, size=1) +  
  viridis::scale_fill_viridis(option = "magma", limits = c(2000,4500))+
  labs(x="Grain Size (µm)", y = "eU (ppm)", title = "Grain size vs. eU" ) +  
  scale_y_continuous(expand=c(0,0), limits=c(0,6600), breaks=seq(0, 6600, 3000)) + 
  scale_x_continuous(expand=c(0,0), limits = c(0,140), breaks=seq(0, 140, 30)) +
  theme_classic() +
  theme(
    panel.border=element_rect(fill=NA,size = 1),
    text = element_text(size = 6),
    legend.position = "none", 
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    plot.title = element_blank(),
    axis.text = element_text(color = "black", size = 6)) +
#ggsave("ME_reU_full.pdf", width = 1.3  , height = 1, units = "in")


ME_reU<-ggplot (data=ME_normal, aes(Grain_size, eU)) + 
  geom_errorbar(aes(ymin=eU-eU_unc, ymax=eU+eU_unc)) +
  geom_point(aes(fill=Elevation), pch=24, size=4) +  
  viridis::scale_fill_viridis(option = "magma", limits = c(2000,4500))+
  labs(x="Grain Size (µm)", y = "eU (ppm)", title = "Grain size vs. eU" ) +  
  scale_y_continuous(expand=c(0,0), limits=c(0,2400), breaks=seq(0, 2400, 400)) + 
  scale_x_continuous(expand=c(0,0), limits = c(0,140), breaks=seq(0, 140, 30)) +
  theme_classic() +
  theme(
    panel.border=element_rect(fill=NA,size = 1),
    text = element_text(size = 12),
    legend.position = "none", 
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.text = element_text(color = "black", size = 12),
    plot.title = element_text(size = 14, hjust = 0.5)) +
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))+
  
#ggsave("ME_reU.pdf", width = 4  , height = 3, units = "in")

####AFT####
MEAFT<-ggplot(data=Evans_AFT, aes(x=AFT_date, y=Elevation))+
  geom_point(pch=2, size=3)+
  geom_errorbarh(aes(xmin=(AFT_date-date_error), xmax=(AFT_date+date_error)), height=0)+
  scale_x_continuous(limits=c(0,800), breaks=seq(0, 800, 200)) + 
  scale_y_continuous(limits = c(2000,4500), breaks=seq(2000, 4500, 500)) +
  labs(x="Date (Ma)", y="Elevation (m)") +
  theme_classic()+
  theme(
    axis.text = element_text(colour = "black"),
    legend.position = c(.85, 0.75))
#ggsave("ME_AFT.pdf", width=5.5, height = 4.5, units = "in", dpi=300)
```

```{r extra ME plots}
MEED<-ggplot (data=ME_normal, aes(date, Elevation)) +
   geom_errorbarh(aes(xmin=date-uncertainty, xmax=date+uncertainty), color = 'black', height=0) +
  geom_point(aes(fill=Elevation), pch=24, size=4) + 
  viridis::scale_fill_viridis(option = "magma")+
  labs(x="Date (Ma)", y = "Elevation (m)", title = "Mount Evans Elevation vs. Date" ) +  
  scale_x_continuous(expand =c(0,0), limits=c(0,800), breaks=seq(0, 800, 200)) + 
  scale_y_continuous(expand =c(0,0),limits = c(2000,4500), breaks=seq(2000, 4500, 500)) +
  theme_classic() + 
  theme(
    panel.border = element_rect(fill=NA, colour = "black", size = 1),
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.title.x = element_text(face="bold", size=12),
    axis.title.y= element_text(face="bold", size=12),
    legend.text = element_text(size = 10),
    axis.text = element_text(color = "black", size = 10), 
    legend.position = c(.9, 0.75),
    plot.title = element_text(size = 14, hjust = 0.5))
   

ME_grainsize<-ggplot (data=ME_normal, aes(Grain_size, date))+
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_point (aes(size=eU, colour=Elevation), shape=17)+
  scale_size("eU")+
  scale_colour_distiller(palette = "RdYlBu", direction = 1, guide = "legend")  +
  scale_y_continuous(expand =c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  scale_x_continuous(expand =c(0,0), limits=c(0,140), breaks=seq(0, 140, 30)) + 
  theme_classic()+
  labs(x="Grain Size (µm)", y = "Date (Ma)", title = "Mt. Evans") +  
  theme(
    panel.border=element_rect(fill=NA,size = 1),
    legend.text = element_text(size = 7), 
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.text = element_text(color = "black", size = 8)) +
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))+
  theme(plot.title = element_text(size = 14, hjust = 0.5))
#ggsave("MEgrain_date1.pdf", width = 4  , height = 3, units = "in", dpi=300)






#This section helped me investigate where the NH4 data was in my data set. Can ignore 
ME_NH4<-ggplot(data=ME_ammonium, aes(x=eU, y=date, fill=Sample_Name))+
  geom_point(color="black", pch=23, size=2)+
  scale_fill_manual(legend_title, values = c("yellow" ,"yellowgreen",  "chartreuse4", "blue2"), guide=guide_legend(reverse = TRUE)) +
  geom_point(data=ME_normal, aes(x=eU, y=date, fill=Sample_Name), pch=2, size = 2 ) +
  theme_classic()

ME_DeUF<-ggplot (data=ME_normal, aes(x=eU, y=date, fill= Sample_Name)) + 
  geom_point(color="black", pch=24, size=3) +  
  scale_fill_manual(legend_title, values = c("yellow" ,"yellowgreen",  "chartreuse4", "blue2"), guide=guide_legend(reverse = TRUE)) +
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_errorbarh(aes(xmin=eU-eU_unc, xmax=eU+eU_unc)) +
  geom_vline(xintercept = 200, color="black", linetype="dashed") + 
  geom_vline(xintercept = 400, color="black", linetype="dashed")  +   
  geom_vline(xintercept = 800, color="black", linetype="dashed")  + 
  labs(x="effective Uranium (ppm)", y = "Date (Ma)", title = "Mt. Evans" ) +  
  scale_x_continuous(limits=c(0,6000), breaks=seq(0, 6000, 1000)) + 
  scale_y_continuous(limits = c(0,900), breaks=seq(0, 800, 900)) +
  theme_classic() +
  theme(
    axis.title.x = element_text(face="bold", size=10), 
    axis.title.y=element_text(face="bold", size=10), 
    axis.text = element_text(colour = "black"),
    legend.position = c(.85, 0.75),
    plot.title=element_text(hjust=0.5)) 

ggplotly(ME_DeUF)

```

```{r}
ME_normal <- mutate(ME_normal, bindata= cut(eU, c(0,400,700,1600,5100))) #these are my bin cutoffs

ME_hefty_flatlist <- ME_normal %>% 
  group_by(bindata) %>% 
    summarize( 
      N = n(),
      RawDate_mean =  round (mean(Raw_Date), digits = 2),
      Rawdate_15percent = round (0.15*mean(Raw_Date), digits = 2),
      Rawdate_SD = round (sd(Raw_Date), digits = 2),
      CorrDate_mean = round(mean(date), digits = 2),
      CorrDate_15percent = round(0.15*mean(date),digits = 2),
      CorrDate_SD = round (sd(date), digits = 2),
      mean_rs = round(mean(Grain_size), digits = 2),
      U = round (mean(U), digits = 2),
      Th = round (mean(Th), digits = 2),
      Sm = round (mean(Sm), digits = 2),
      eU = round (mean(eU), digits = 2),
      He = round (mean(He), digits = 2),
      FT = round (mean(FT), digits = 2),
      )

write.csv(ME_hefty_flatlist, file="Evans Hefty Flatlist.csv")
```



This section plots:
1. LP Date eU (Johnson thesis, 2015)
2. LP elevation date (Johnson thesis, 2015)
3. LP AFT data (kelley and chapin, 2004)
```{r PLot Longs Peak Data}
####Date eU and Date Elevation####
LP_DeU<-ggplot (data=Longs_Peak, aes(x=eU, y=date)) + 
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) +
  geom_errorbarh(aes(xmin=eU-eU_unc, xmax=eU+eU_unc)) +
  geom_point(aes(fill=Elevation), pch=23, size=4) +
  viridis::scale_fill_viridis(option = "magma", limits = c(2000,4500))+
  #geom_vline(xintercept = 200, color="black")  + geom_vline(xintercept = 600, color="black")  + geom_vline(xintercept = 1000, color="black")  + 
  labs(x="effective Uranium (ppm)", y = "Date (Ma)", title = "Longs Peak" ) +  
  scale_x_continuous(expand=c(0,0), limits=c(0,2400), breaks=seq(0, 2400, 400)) + 
  scale_y_continuous(expand=c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  theme_classic()+
  theme(
   panel.border = element_rect(fill=NA, colour = "black", size = 1),
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.title.x = element_text(face="bold", size=12),
    axis.title.y= element_text(face="bold", size=12),
    legend.text = element_text(size = 10),
    axis.text = element_text(color = "black", size = 10), 
    legend.position = "none",
    plot.title = element_text(size = 14, hjust = 0.5))+
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))
#ggsave("LPdate_eU.pdf", width = 4  , height = 3, units = "in")


LP_ED_byeU<-ggplot(data=Longs_Peak, aes(date, Elevation))+
  geom_errorbarh(aes(xmin=date-uncertainty, xmax=date+uncertainty), color = 'black', height=0)+
  geom_point(aes(fill=eU), shape=23, size=4)+
  viridis::scale_fill_viridis(option = "viridis", limits=c(0,2000))+
  geom_point(data=Longs_AFT, aes(AFT_date, Elevation), pch=18, size=4)+
  theme_classic()+
  labs(x="Date (Ma)", y = "Elevation (m)", title = "Longs Peak") +  
  scale_x_continuous(expand =c(0,0), limits=c(0,800), breaks=seq(0, 800, 200)) + 
  scale_y_continuous(expand =c(0,0), limits = c(2000,4500), breaks=seq(2000, 4500, 500))+
  theme(
    panel.border = element_rect(fill=NA,  colour = "black", size = 1),
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.title.x = element_text(face="bold", size=12),
    axis.title.y= element_text(face="bold", size=12),
    legend.text = element_text(size = 10),
    axis.text = element_text(color = "black", size = 10), 
    legend.position = c(.9, 0.75),
    plot.title = element_text(size = 14, hjust = 0.5)) +
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))
#ggsave("LPelevation_date.pdf", width = 4  , height = 3, units = "in", dpi=300)

####Grain Size####
#Grain size w/ color as Elevation 
LP_rDate<-ggplot (data=Longs_Peak, aes(Grain_size, date))+
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_point (aes(fill=Elevation), shape=23, size =4)+
  viridis::scale_fill_viridis(option = "magma", limits = c(2000,4500))+
  theme_classic()+
  scale_y_continuous(expand =c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  scale_x_continuous(expand =c(0,0), limits=c(0,140), breaks=seq(0, 140, 30)) + 
  labs(x="Grain Size (µm)", y = "Date (Ma)", title = "Longs Peak") +  
  theme(
    panel.border=element_rect(fill=NA,size = 1),
    text = element_text(size = 12),
    legend.position = "none", 
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.text = element_text(color = "black", size = 12)) +
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight =2))+
  theme(plot.title = element_text(size = 14, hjust = 0.5))
#ggsave("LP_rDate.pdf", width = 4  , height = 3, units = "in", dpi=300)

#Grain size vs. eU
LP_reU<-ggplot (data=Longs_Peak, aes(Grain_size, eU)) + 
  geom_errorbar(aes(ymin=eU-eU_unc, ymax=eU+eU_unc)) +
  geom_point(aes(fill=Elevation), pch=23, size=4) +
  viridis::scale_fill_viridis(option = "magma", limits = c(2000,4500))+
  labs(x="Grain Size (µm)", y = "eU (ppm)", title = "Longs Peak" ) +  
  scale_y_continuous(expand=c(0,0), limits=c(0,2400), breaks=seq(0, 2400, 400)) + 
  scale_x_continuous(expand=c(0,0), limits = c(0,140), breaks=seq(0, 140, 30)) +
  theme_classic()+
  theme(
    panel.border=element_rect(fill=NA,size = 1),
    text = element_text(size = 12),
    legend.position = "none", 
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.text = element_text(color = "black", size = 12)) +
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))
#ggsave("LP_reU.pdf", width = 4  , height = 3, units = "in")

####AFT####
LPAFT<-ggplot(data=Longs_AFT, aes(x=AFT_date, y=Elevation))+
  geom_point(pch=5, size=3)+
  geom_errorbarh(aes(xmin=(AFT_date-date_error), xmax=(AFT_date+date_error)), height=0)+
  scale_x_continuous(limits=c(0,800), breaks=seq(0, 800, 200)) + 
  scale_y_continuous(limits = c(2000,4500), breaks=seq(2000, 4500, 500)) +
  labs(x="Date (Ma)", y="Elevation (m)") +
  theme_classic()+
  theme(
    axis.text = element_text(colour = "black"),
    legend.position = c(.85, 0.75))
#ggsave("LP_AFT.pdf", width=5.5, height = 4.5, units = "in", dpi=300)
```

```{r extra LP plots}
####Elevation Date####
LPED<-ggplot (data=Longs_Peak, aes(x=date, y=Elevation, fill=Sample_Name)) +
  geom_errorbarh(aes(xmin=date-uncertainty, xmax=date+uncertainty), color = 'black', height=0) +
  geom_point(color="black", pch=23, size=3) + 
  labs(x="Date (Ma)", y = "Elevation (m)", title = "Longs Peak" ) +  
  scale_x_continuous(limits=c(0,800), breaks=seq(0, 800, 200)) + 
  scale_y_continuous(limits = c(2000,4500), breaks=seq(2000, 4500, 500)) +
   theme_classic()+
  theme(
    axis.title.x = element_text(face="bold", size=10), 
    axis.title.y=element_text(face="bold", size=10), 
    axis.text = element_text(color="black"),
    legend.position = c(.9, 0.75),
    plot.title=element_text(hjust=0.5))
#ggsave("LPelevation_date.pdf", width = 5.5  , height = 4.5, units = "in", dpi=300)

#Grain size w/ color designation as Elevation and size as eU 
LP_grainsize<-ggplot (data=Longs_Peak, aes(Grain_size, date))+
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_point (aes(size=eU, colour=Elevation), shape=18)+
  scale_size("eU")+
  viridis::scale_fill_viridis(option = "magma", limits = c(2000,4500))+
  scale_y_continuous(expand =c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  scale_x_continuous(expand =c(0,0), limits=c(0,140), breaks=seq(0, 140, 30)) + 
  theme_classic()+
  labs(x="Grain Size (µm)", y = "Date (Ma)", title = "Longs Peak") +  
  theme(
    panel.border=element_rect(fill=NA,size = 1),
    text = element_text(size = 12),
    legend.text = element_text(size = 10), 
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    plot.title = element_text(size = 14, hjust = 0.5),
    axis.text = element_text(color = "black", size = 12)) +
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))+



#Grain size w/ color designation as eU 
LP_grainsize_eU<-ggplot (data=Longs_Peak, aes(Grain_size, date))+
  geom_errorbar(aes(ymin=date-uncertainty, ymax=date+uncertainty), color = 'black', width=.1) + 
  geom_point (aes(fill=eU), shape=23, size=4)+
  viridis::scale_fill_viridis(option = "magma", limits = c(2000,4500))+
  theme_classic()+
  scale_y_continuous(expand =c(0,0), limits = c(0,800), breaks=seq(0, 800, 200)) +
  scale_x_continuous(expand =c(0,0), limits=c(0,140), breaks=seq(0, 140, 30)) + 
  labs(x="Grain Size (µm)", y = "Date (Ma)", title = "Longs Peak") +  
  theme(
    panel.border=element_rect(fill=NA,size = 1),
    text = element_text(size = 12),
    legend.position = "none", 
    axis.ticks = element_line(color="black"),
    axis.line = element_line(color = NA),
    axis.text = element_text(color = "black", size = 12)) +
  guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2))
  
#ggsave("LPdate_grain_eU.pdf", width = 4  , height = 3, units = "in", dpi=300)


```

